\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\renewcommand{\baselinestretch}{1.3}

\title{Sr. Design Proposal}
\author{Brian Rappaport, Anuththari Gamage, Shuchin Aeron }
\date{July 2017}

\begin{document}

\maketitle

The goal of this project is to investigate graph clustering algorithms based upon pairwise interaction data among entities. Such scenarios arise in disciplines as varied as natural language processing for machine translation and interpretation, biological systems of protein-protein interactions, or community detection in social networks. Specifically we will investigate several methods from classical Spectral Clustering to cutting-edge methods such as using the Diffusion State Distance metric on networks and embedding the nodes of a graph in Euclidean space via the well-known word2vec deep learning architecture. The final deliverable will be a suite of algorithms in Python and MATLAB that are computationally efficient, reliable, and robust to many types of data, as well as a rich variety of datasets and a detailed, well organized literature survey for bringing in future researchers to this exciting and important work.
Anyone interested in being a part of this project should have a strong mathematical background, especially in linear algebra, and be prepared to survey recent literature in machine learning and statistics. A background in algorithm design and optimization would also be appreciated. The focus will be mainly on software rather than hardware.

\end{document}